---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Looking more closely at the data

```{r}
agg_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Let's start by doing a `prop.test()` for one city.

```{r}
prop.test(
  agg_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  agg_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
    ) %>% 
  broom::tidy()
```

Let's iterate this

```{r}
results_df = 
  agg_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Making a graph

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Loading in 20 datasets and tidying data.

```{r}
path_df = 
  tibble(
  path = list.files(path = "lda_data")
  ) %>% 
  mutate(path = str_c("lda_data/", path),
         data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(data) %>% 
  mutate(arm_id = recode(path, "lda_data/con_01.csv" = "control_01", "lda_data/con_02.csv" = "control_02", "lda_data/con_03.csv" = "control_03", "lda_data/con_04.csv" = "control_04", "lda_data/con_05.csv" = "control_05", "lda_data/con_06.csv" = "control_06", "lda_data/con_07.csv" = "control_07", "lda_data/con_08.csv" = "control_08", "lda_data/con_09.csv" = "control_09", "lda_data/con_10.csv" = "control_10", "lda_data/exp_01.csv" = "experimental_01", "lda_data/exp_02.csv" = "experimental_02", "lda_data/exp_03.csv" = "experimental_03", "lda_data/exp_04.csv" = "experimental_04", "lda_data/exp_05.csv" = "experimental_05", "lda_data/exp_06.csv" = "experimental_06", "lda_data/exp_07.csv" = "experimental_07", "lda_data/exp_08.csv" = "experimental_08", "lda_data/exp_09.csv" = "experimental_09", "lda_data/exp_10.csv" = "experimental_10",)) %>% 
  separate(arm_id, into = c("arm", "subject_id"), sep = "_", convert = T) %>% 
  select(-path) %>% 
   select(arm, subject_id, everything()) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "observations"
  )
```


```{r}
graph = 
  path_df %>% 
  ggplot(aes(x = week, y = observations, group = subject_id, color = subject_id))+
  geom_point()+
  geom_line()+
  facet_grid(. ~ arm)

graph
```

The experimental group of subjects seemed to have the observed values increase over the eight weeks, while the control group on the whole did not appear to have much meaningful change in observed values. Some subjects in the control group appeared to have an increase in values, while others had decreasing values, and still others had values that remained the same across the eight weeks of observations. The range of starting values for the control group seemed closer together as compared to the experimental group, which seemed to have a wider range of starting observed values.

##Problem 3


```{r}
okur = function(n = 30, mu = 0, sigma = 5) {
  sim_data =
    tibble(
      x = rnorm(n = n, mean = mu, sd = sigma)
    ) %>% 
    t.test(alternative = 'two.sided', paired = FALSE, conf.level = 0.95) %>% 
    broom::tidy()
}

rerun(5000, okur(mu = 0)) %>% 
  bind_rows() %>% 
  select(estimate, p.value)

mu_list = 
  list(
    "mu = 1" = 1,
    "mu = 2" = 2,
    "mu = 3" = 3,
    "mu = 4" = 4,
    "mu = 5" = 5,
    "mu = 6" = 6
  )

```

Getting the first plot - proportion of times the null was rejected vs. mean

```{r}
output = vector("list", length = 6)

for (i in 1:6) {
output[[i]] = 
  rerun(5000, okur(mu = mu_list[[i]])) %>% 
  bind_rows() %>% 
  select(estimate, p.value) %>% 
  summarize(
    total = n(),
    reject_null = sum(p.value <= 0.05),
    mu = mu_list[[i]]
  )
}

df_pt1 = 
  as.data.frame(do.call(rbind, lapply(output, function(x) { unlist(x)}))) %>% 
  mutate(proportion = reject_null/total) %>% 
  select(-total, -reject_null)

df_pt1 %>% 
  ggplot(aes(x = mu, y = proportion))+
  geom_point()+
  geom_line()

```

It appears that as the true value of mu increases, the proportion of times that the null was rejected exponentially increases, which represents an increase in power. This graph seems to indicate that effect size and power have a positive relationship, so as one increases, the other increases as well.
